article title

### 2022-07-25 pilon_gilles_glossary.tex
Add individuals chart
Add moving range chart

    description={It is a process behaviour chart that plots the average of a subgroup of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line and an average line.},

@@

>>>>

    description={It is a process behaviour chart that plots the average of a subgroup of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line, and an average line.},

@@

\newglossaryentry{individuals_chart}
    name={individuals chart},
    description={It is a process behaviour chart that plots the single values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line, and an average line.},
    plural={individuals charts}
\newglossaryentry{moving_range_chart}
    name={moving range chart},
    description={It is a process behaviour chart that plots the difference between successive pairs of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line, and an average line.}
    plural={moving range charts}
